Causal analysis of COVID-19 observational data in German districts reveals effects of mobility, awareness, and temperature

### 2020-07-22 manuscript/v2_medrxiv/manuscript.tex
insert acknowledgments

Furthermore, we made a strong case for the use of causal DAGs in epidemiology and a pandemic like COVID-19: DAGs allow to choose confounders for the analysis in a principled and statistically correct way while reducing possible causes for bias. Also, the DAG formalization allows for discussion about the underlying causal structure.

@@

>>>>

Furthermore, we made a strong case for the use of causal DAGs in epidemiology and a pandemic like COVID-19: DAGs allow to choose confounders for the analysis in a principled and statistically correct way while reducing possible causes for bias. Also, the DAG formalization allows for discussion about the underlying causal assumptions.

@@

\hypertarget{acknowledgments}{%
\section*{Acknowledgments}\label{acknowledgments}}
\addcontentsline{toc}{section}{Acknowledgments}

We are thankful for feedback from Thomas Czihal, Johannes Textor, and Ralph Brinks, who gave helpful suggestions on an earlier draft of the manuscript.
